Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-14 snapshot_system/snapshot.tex
revise

%A deduplication scheme compares the fingerprints of the current snapshot
%with its parent snapshot and also other snapshots in the entire cloud.
%The traditional approach compares all fingerprints and 
%stores one copy for all of a chunk's duplicates.
%We call this as  the VM-oblivious (VO) approach.
Our VC design has the following  objectives: 1)  localizing deduplication while identifying a decent amount of
duplicates among VMs to maintain a competitive deduplication efficiency and simplify snapshot management;
2) Minimizing the number of file system blocks shared among VMs and adding extra replicas for shared blocks.

@@

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??},  
%This allows the system to achieve deduplication even when there are insertions/deletions which would
%affect many fixed-size chunks.
we conduct additional local inner-VM deduplication by comparing
dirty segment's chunk fingerprints to similar segments from its parent snapshot. 
For every segment, the minimum value of all its chunk fingerprints is computed during backup
and is recorded in the snapshot recipe.
When we are processing a dirty segment,
we can easily find similar segments from the
parent snapshot recipe and load their segment recipes. Then 
given a set of data chunks within a dirty segement,  we compare  these chunk fingerprints
with those in similar segments.  
For example, with a 2MB segment, there are about 500 fingerprints to compare.
The amount of memory for maintaining those fingerprints in similar segment s is small, as we only
load one dirty segment at a time.

>>>>

%A deduplication scheme compares the fingerprints of the current snapshot
%with its parent snapshot and also other snapshots in the entire cloud.
%The traditional approach compares all fingerprints and 
%stores one copy for all of a chunk's duplicates.
%We call this as  the VM-oblivious (VO) approach.

%Our VC design has the following  objectives: 1)  localizing deduplication while identifying a decent amount of
%duplicates among VMs to maintain a competitive deduplication efficiency and simplify snapshot management;
%2) Minimizing the number of file system blocks shared among VMs and adding extra replicas for shared blocks.

@@

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??},  
%This allows the system to achieve deduplication even when there are insertions/deletions which would
%affect many fixed-size chunks.
we conduct additional local inner-VM deduplication by comparing
dirty segment's chunk fingerprints within  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their approximated content signature is the same.
This segment signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot recipe.
When we are processing a dirty segment,
we can easily find similar segments from the
parent snapshot recipe and load their segment recipes and also set a limit on the 
the number of  similar segments to be  searched. 
 Then 
given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
with those in similar segments.  
For example, with a 2MB segment, there are about 500 fingerprints to compare. By limiting at most 10 similar
segments to search,
the amount of memory for maintaining those fingerprints in similar segment s is small.
% as we only load one dirty segment at a time.
